---
title: "ACA Grants in Research and Biodiversity, 1997-2017"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(tidyverse)
library(RColorBrewer)
library(bibliometrix)
##library(maps)
##library(mapdata)
##library(ggthemes)
##library(gganimate)
library(leaflet)
library(flexdashboard)

## Read in prepared indices
authorList <- tail(read.csv("Data/ACA Author Index 1997-2017 - ACA author index.csv", header=TRUE, stringsAsFactors = FALSE), -1)
authorList$ACA.publications <- as.numeric(authorList$ACA.publications)

grantList <- read.csv("Data/ACA Grants Index 1997-2017 - ACA Grants Index.csv", header = TRUE)
names(grantList) <- str_remove_all(names(grantList), "[.]")

pubList <- read.csv("Data/ACA Publication Index 1997-2017 - Publication index.csv")
```

Citation and Altmetrics
=====================================

Column {data-width=500}
-------------------------------------
### Fig. 1

```{r citation-by-year}
citation_by_year <- pubList %>% 
     group_by(Year) %>% 
     summarise(cites = sum(as.integer(Citation.count))) 

fig1 <- ggplot(citation_by_year, aes(x=Year, y=cites)) + geom_col() + theme_classic() + labs(title="Citations by Year of Publication", x="Publication Year", y="Number of Citations")

fig1
```

### Fig. 2

```{r publication-by-year}
publication_by_year <- pubList %>%
    group_by(Year) %>%
    summarise(articles = n())

fig2 <- ggplot(publication_by_year, aes(x=Year, y=articles)) + geom_col() + theme_classic() + labs(title = "Number of Publications by Year", x="Publication Year", y="Articles") + geom_line(data = citation_by_year, aes(x=Year, y=cites/25, colour = "red"), show.legend = FALSE) + scale_y_continuous(sec.axis = sec_axis(~ . *20, breaks = waiver(), labels = waiver(), name = "Citations"))

fig2
```

Column {data-width=500}
-------------------------------------
### Fig. 3

```{r tweets-by-year-and-category}
levels(pubList$Category)[1] <- "Not assigned"

categoryPalette <- colorRampPalette(brewer.pal(7,"Dark2"))(14)

fig3 <- ggplot(pubList, aes(x=Year, y=Twitter)) + geom_point(aes(col=Category, size=Twitter)) + theme_classic() + labs(title="Tweets and ReTweets of ACA-funded Publications", y="Number of Tweets and ReTweets", x="Year of Publication") + scale_colour_manual(values = categoryPalette)
 
fig3
```

### Author List 

```{r Author-table}

ACAauthors <- subset(authorList, ACA.publications != 0)
ACAauthors$ACA.publications <- as.numeric(ACAauthors$ACA.publications)
library(DT)
DT::datatable(ACAauthors[,c("Last.name", "First.name", "ACA.publications")], rownames = FALSE, options = list(pageLength = 10))
```

Overview of Grants
=====================================

Map of grant locations

Column {data-width=600}
-------------------------------------
```{r location-data}
## Gather data for grant mapping
## Create data frame of locations and assigned longitude and lattitude

locations <- as.tibble(cbind(c("Banff National Park", "CFB Suffield", "Elk Island National Park", "Foothills", "Jasper National Park", "Mountain", "Northern Boreal", "Parkland", "Prairie", "Waterton Lakes National Park", "Wood Buffalo National Park", "Unknown", ""), c("-115.92797", "-111.175004", "-112.857157", "-116.817049", "-117.954272", "-116.476799", "-116.569466", "-111.575478", "-112.336827", "-113.916624", "-112.876509", "-113.528040", "-113.528040"), c("51.496746", "50.277093", "53.608301", "54.187166", "52.873331", "52.37858", "57.015187", "52.990867", "50.583973", "49.083404", "59.439519", "53.526210", "53.524449")))

colnames(locations) <- c("location", "lng", "lat")

locations$location <- as.factor(locations$location)
locations$lng <- as.numeric(locations$lng)
locations$lat <- as.numeric(locations$lat)

grantsperLoc <- count(grantList, CodedLocation, YearAwarded) %>%
    left_join(locations, b=c("CodedLocation" = "location"))


##grantsperTopic <- count(grantList, DetailedThematicCategory, YearAwarded) %>%
##    left_join(locations, b=c("CodedLocation" = "location"))

##grantsperPriorityArea <- count(grantList, ACARGPriorityAreas1, YearAwarded) %>%
##    left_join(locations, b=c("CodedLocation" = "location"))

## create base map

library(sf)
Alberta <- sf::st_read("GEO_Admin_SHP_Geographic/bf_geoadmin_15-10-2018/Wildlife Management Unit.shp")
plot(Alberta)

Alberta$
```

Column {data-width=400}
-------------------------------------

### Grant List

```{r Grant-table}

library(DT)
DT::datatable(grantList[,c("CurrentGrantName", "YearAwarded", "GrantValue", "ProjectTitle", "CodedLocation")], rownames = FALSE, filter = "top", options = list(pageLength = 10))
```

Bibliometric Visualizations
=====================================

```{r bibliometric-data-load, include=FALSE}
# Loading bib files into R environment
D <- readFiles("Data/scopus.bib")

# Converting the loaded files into a R bibliographic dataframe
M <- convert2df(D, dbsource="scopus",format="bibtex")
```

### Section 1: Descriptive Analysis

Bibliometrix is an open-source software package for automating the stages of data-analysis and data-visualization developed by Massimo Aria and Corrado Cuccurullo. After converting and uploading bibliographic data in R, Bibliometrix performs a descriptive analysis and different research-structure analyses.

Descriptive analysis provides some snapshots about the annual research development, the top "k" productive authors, papers, countries and most relevant keywords.

### Main findings about the collection

```{r}
results <- biblioAnalysis(M)
summary(results, k=10, pause=F, width=130)
plot(x=results, k=10, pause=F)
```
