---
title: "ACA Grants in Research and Biodiversity, 1997-2017"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(tidyverse)
library(RColorBrewer)
library(bibliometrix)
library(maps)
library(mapdata)
library(ggthemes)
library(gganimate)
library(flexdashboard)

## Read in prepared indices
authorList <- read.csv("Data/ACA Author Index 1997-2017 - ACA author index.csv", header=TRUE)
grantList <- read.csv("Data/ACA Grants Index 1997-2017 - ACA Grants Index.csv", header = TRUE)
pubList <- read.csv("Data/ACA Publication Index 1997-2017 - Publication index.csv")
```
Citation and Altmetrics
=====================================

### Chart 1

```{r citation-by-year}
citation_by_year <- pubList %>% 
     group_by(Year) %>% 
     summarise(cites = sum(as.integer(Citation.count))) 

fig1 <- ggplot(citation_by_year, aes(x=Year, y=cites)) + geom_col() + theme_classic() + labs(title="Citations by Year of Publication", x="Publication Year", y="Number of Citations")

fig1
```

### Chart 2

```{r publication-by-year}
publication_by_year <- pubList %>%
    count(Year)

fig2 <- ggplot(publication_by_year, aes(x=Year, y=n)) + geom_col() + theme_classic() + labs(title = "Number of Publications by Year", x="Publication Year", y="Number of articles")

fig2
```

### Chart 3

```{r tweets-by-year-and-category}
levels(pubList$Category)[1] <- "Not assigned"

categoryPalette <- colorRampPalette(brewer.pal(7,"Dark2"))(14)

fig3 <- ggplot(pubList, aes(x=Year, y=Twitter)) + geom_point(aes(col=Category, size=Twitter)) + theme_classic() + labs(title="Tweets and ReTweets of ACA-funded Publications", y="Number of Tweets and ReTweets", x="Year of Publication") + scale_colour_manual(values = categoryPalette)
 
fig3
```

Overview of Grants
=====================================
Placeholder text describing the output on this page.
```{r location-data}
## Gather data for grant mapping
## Create data frame of locations and assigned longitude and lattitude

locations <- as_tibble(cbind(c("Banff National Park", "CFB Suffield", "Elk Island National Park", "Foothills", "Jasper National Park", "Mountain", "Northern Boreal", "Parkland", "Prairie", "Waterton Lakes National Park", "Wood Buffalo National Park"), c("-115.92797", "-111.175004", "-112.857157", "-116.817049", "-117.954272", "-116.476799", "-116.569466", "-111.575478", "-112.336827", "-113.916624", "-112.876509"), c("51.496746", "50.277093", "53.608301", "54.187166", "52.873331", "52.37858", "57.015187", "52.990867", "50.583973", "49.083404", "59.439519")))

colnames(locations) <- c("location", "lon", "lat")


```

Bibliometric Visualizations
=====================================

```{r bibliometric-data-load, include=FALSE}
# Loading bib files into R environment
D <- readFiles("Data/scopus.bib")

# Converting the loaded files into a R bibliographic dataframe
M <- convert2df(D, dbsource="scopus",format="bibtex")
```

### Section 1: Descriptive Analysis

Bibliometrix is an open-source software package for automating the stages of data-analysis and data-visualization developed by Massimo Aria and Corrado Cuccurullo. After converting and uploading bibliographic data in R, Bibliometrix performs a descriptive analysis and different research-structure analyses.

Descriptive analysis provides some snapshots about the annual research development, the top "k" productive authors, papers, countries and most relevant keywords.

### Main findings about the collection

```{r}
results <- biblioAnalysis(M)
summary(results, k=10, pause=F, width=130)
plot(x=results, k=10, pause=F)
```
